Variation in distance between consecutive animal locations

### 2021-04-15 distributions_paper/rudolph_distributions.Rmd
Progress with results

## Example: Many-banded aracari movement

# Results  
The majority of trajectories obtained were regular, with 15 minute time lags between successive relocations, however, some relocations were gathered at different time intervals, making them irregular. To analyze all trajectories and compare their descriptive parameters, we decided to work under a velocity-based framework.

<span style="color:red">For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and we calculated turning angles (in radians), and the associated Euclidean step lengths in meters for each successive set of locations and turning directions. We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded. This gave us a total of **600ish?** data points for turning angles and velocities.red</span>

What do we consider a trajectory? The path followed by consecutive relocations during a tracking session. The tracking session for this data is the 4-5 hour period each day that they follow the bird. Then, the number of relocations for each trajectory varies from one to 26, with a mean of 4 relocations. This is a limitation of the data, since it's not easy to characterize a full trajectory of movement with such a small number of relocations in a trajectory.

Dealing with the issue of autocorrelation in this case: what does that mean? Or we just assume each step is independent from the others. Think I saw this in the Kareiva Shigesada paper. 
```{r eval=FALSE}
# For this to run I need to move the load of data and such higher up
aracari_df %>%
  group_by(id, burst) %>% 
  tally() -> relocs

# Having a minimum number of relocations for "time series analysis" or something, fitting.
relocs %>% 
  filter(n >= 5) %>% 
  distinct(id)

relocs %>% 
  ggplot(., aes(x = n, fill = id)) +
  geom_histogram()
summary(relocs$n)
```

```{r eval=FALSE}
aracari_df %>% 
  filter(R2n >0) %>% 
  ggplot(., aes(x = R2n)) +
  geom_histogram() +
  facet_wrap(~id)
```

**Could I find anything pre HMMs of SSMs? Wondering what people could do before? And wondering this because we have broken up tracking periods, not continuous ones**  
Seems like I need to focus more on random walks

@@

Consider incorporating NAs for missed observations so we keep the regular 15 minute time interval.

@@

```{r setup, include=FALSE}
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, 
                      eval=FALSE,
                      echo = FALSE)

@@

```{r eval=FALSE}
# Which individuals will we conside? Need at least a certain number of data points to fit distributions
# Don't remove any yet, just make sure you make it clear how many data points you have for each

aracari_df %>% 
  dplyr::filter(dist != 0) %>% 
  group_by(id) %>% 
  tally()

aracari_df %>% 
  mutate(tmin = dt/60,
         mpm = dist/tmin) %>% 
  drop_na(tmin) %>% 
  filter(tmin == 60) %>% 
  group_by(id) %>% 
  tally() %>% 
  filter(n >=20)

@@

```{r eval=FALSE}
focus <- "dist15"

df <- aracari_df %>%
  mutate(tmin = dt/60,
         mpm = dist/tmin,
         Bird_ID = paste0("B", id),
         focus = mpm) %>% 
  drop_na(tmin) %>% 
  filter(tmin == 15) %>% 
  dplyr::filter(dist != 0) %>% 
  group_by(id) %>%
  filter(., n() >= 20) %>%
  ungroup()

  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
  kpars <- c(1, 2, 2, 2, 2, 2, 2)
```

```{r eval=FALSE}
df %>% 
  ggplot(., aes(x = abs.angle)) +
  geom_histogram() +
  facet_wrap(~Bird_ID)
```

```{r eval=FALSE}
df %>%
  drop_na(rel.angle) %>%
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>%
  ggplot(., aes(x = d.angle)) +
  #facet_wrap(~id) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none")
```

```{r}
# Create my focus variable and only for individuals with 30+ observations

# focus <- "dist"
# focus <- "R2n"
 focus <- "mpm"
# focus <- "m15"

if(focus == "dist"){
  df <- aracari_df %>%
  dplyr::filter(dist != 0) %>%
  group_by(id) %>%
  filter(., n() >= 30) %>%
  ungroup() %>%
  dplyr::filter(dist != 0) %>% 
    mutate(Bird_ID = paste0("B", id),
           focus = dist)

  dist.used <- c("lnorm", "weibull", "cauchy")
  param <- c("meanlog", "sdlog", "shape", "scale", "location", "scale")
  dist <- c("lnorm", "lnorm", "weibull", "weibull", "cauchy", "cauchy")
  kpars <- c(2, 2, 2, 2, 2, 2)
}

if(focus == "R2n"){
  df <- aracari_df %>%
  dplyr::filter(R2n != 0) %>%
  group_by(id) %>%
  filter(., n() >= 30) %>%
  ungroup() %>%
  dplyr::filter(R2n != 0) %>% 
    mutate(Bird_ID = paste0("B", id),
           focus = sqrt(R2n))

  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
  kpars <- c(1, 2, 2, 2, 2, 2, 2)
}

if(focus == "mpm"){
  df <- aracari_df %>% 
  dplyr::filter(dist != 0) %>% 
  group_by(id) %>%
  filter(., n() >= 30) %>%
  ungroup() %>%
  mutate(tmin = dt/60,
         mpm = dist/tmin,
         Bird_ID = paste0("B", id),
         focus = mpm) %>% 
  dplyr::filter(., mpm != 0)

  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
  kpars <- c(1, 2, 2, 2, 2, 2, 2)
}

if(focus == "m15"){
  df <- aracari_df %>% 
  dplyr::filter(dist != 0) %>% 
  group_by(id) %>%
  filter(., n() >= 30) %>%
  ungroup() %>%
  mutate(tmin = dt/60,
         mpm = dist/tmin,
         m15 = mpm*15,
         Bird_ID = paste0("B", id),
         focus = m15) %>% 
  dplyr::filter(., m15 != 0)

  dist.used <- c( "exp", "gamma", "weibull", "lnorm")
  param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
  dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
  kpars <- c(1, 2, 2, 2, 2, 2, 2)
}

@@

\newpage

### MPM: meters per minute
Due to the variation in time between consecutive locations, we scaled the step lengths to displacement in one minute.
**Visualize the variation and distribution of these distances between locations**

```{r}
 df %>%
  ggplot(., aes((x = focus))) +
  geom_line(aes(x = focus, group = id), stat = "density", alpha = 0.4) +
  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = paste(focus)) +
  theme_classic()

@@

```{r}
df %>%
  ggplot(., aes(x = focus)) +
  facet_wrap(~id) +
  geom_line(stat = "density") +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = paste(focus)) +
  theme_classic()
```

# Fit distribution

@@

pop <- lapply(dist.used, function(x){fitdist(df$focus, distr = x)})

@@

# Repeating the process for data at the individual level
inds <- unique(as.character(df$Bird_ID))

# Fitting the four distributions for each individual and saving the parameters in a dataframe
ind.models <- NULL
for(i in 1:length(inds)){
  fit.df <- df %>% 
    dplyr::filter(., Bird_ID == inds[i])

  fit <- lapply(dist.used, function(x){fitdist(fit.df$focus, distr = x)})

@@

@@

qqpop %>% 
  mutate(individual = "POPULATION") %>% 
  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
  facet_wrap(~individual) +
  #coord_equal() +
  geom_point(shape = 16, alpha = 0.8, size = 4) +
  geom_abline(intercept = 0, slope = 1) +
  labs(x = "Model Quantiles",
         y = "Empirical Quantiles") +
  #scale_color_viridis_d() +
  scale_color_brewer(palette = "Spectral", name = "Distribution") +
  theme(legend.position = c(0.8, 0.2)) +
  NULL -> a

@@

## Information criteria

@@

prms.df %>% 
  mutate(param = str_to_upper(param), 
         dist = str_replace(dist, "exp", "Exponential"),
         dist = str_replace(dist, "gamma", "Gamma"),
         dist = str_replace(dist, "weibull", "Weibull"),
         dist = str_replace(dist, "lnorm", "Lognormal"),
         data = str_replace(data, "pop", "POP")) %>% 
  mutate(BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
  mutate(best_bic = ifelse(deltaBIC == 0, "#ffaa00", "black"),
         best_aic = ifelse(deltaAIC == 0, "#fc0362", "black")) -> nice_prms
```

```{r}
nice_prms %>% 
  filter(., str_detect(data, "B")) %>% 
  dplyr::select(dist, data, deltaAIC,
                #deltaAICc,
                deltaBIC) %>% 
  distinct() %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  filter(value == 0) %>%  
  pivot_wider(., names_from = ic, values_from = dist) %>% 
  mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
  dplyr::select(., data, agree) %>% 
  rename(Individual = data,
            `Best model` = agree) -> best_model

knitr::kable(best_model)
# 
# 
# nice_prms %>% 
#   filter(., data != "pop") %>% 
#   dplyr::select(dist, data, deltaAIC,
#                 #deltaAICc,
#                 deltaBIC) %>% 
#   distinct() %>% 
#   pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
#   filter(value > 0 & value <= 2) %>%  
#   pivot_wider(., names_from = ic, values_from = dist) %>% 
#   mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
#   dplyr::select(., data, agree) %>% 
#   rename(Individual = data,
#             `Best model` = agree)

@@

However, it is not as straight-forward since there are multiple competing models for certain individuals, which we consider as those within less than 2 units of the delta AIC or BIC. When using AIC, there are competing models for almost every individual, whereas with BIC, only 4 of the individuals have competing models. We should use 4 for BIC and 3 for AIC. Look for the paper Taper Ponciano 2016. 
```{r fig.width=12, fig.height=4}
# To visualize the differences in the information criteria at the individual level

```
Now we can compare what we call *models*, in which we compare a model that does complete pooling and considers all the data together, and the other model that considers individual variation, and so it fits a separate distribution to the data from each individual.

The individual variation models will fit a distribution to each individual. At one level we will use the same distribution for all individuals and only consider variation in parameters. At the next level, we will consider a change in parameters and distributions, where individuals can have different distributions, and this is what we call the mixed distribution model for individual variation.

@@

Considering just focusing on BIC because of JMP's paper, and also in this specific case, it provides less competing models for each individual
```{r}
# Table for BIC and AIC only

@@

gt_tbl %>% 
  tab_header(
    title = md("**Model comparisons across levels**")
  ) %>% 
  tab_stubhead(label = "Model") %>% 
  tab_row_group(
    group = "Multidist",
    rows = 9
  ) %>% 
  tab_row_group(
    group = "Individual",
    rows = 1:4
  ) %>% 
  tab_row_group(
    group = "Population", 
    rows = 5:8
  ) %>% 
  tab_spanner(
    label = md("**BIC**"),
    columns = vars(BIC, delta_BIC_within, delta_BIC_across)
  ) %>% 
  tab_spanner(
    label = md("**AIC**"),
    columns = vars(AIC, delta_AIC_within, delta_AIC_across)
  ) %>% 
  cols_label(
    delta_BIC_within = html("&Delta; BIC<sub>within</sub>"),
    delta_BIC_across = html("&Delta; BIC<sub>across</sub>"),
    delta_AIC_within = html("&Delta; AIC<sub>within</sub>"),
    delta_AIC_across = html("&Delta; AIC<sub>across</sub>")
  ) -> gt_table_bic

@@

## Probability distribution parameters
We can compare the different parameter values estimated for each distribution and their standard deviations. These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute. The x axis in the following plots highlights which individuals have the lowest BIC (yellow) or AIC(magenta) with that model. The blue lines show the value of that parameter for the population level model, and dashed blue lines show the upper and lower limits of that parameter estimate. Overall, at the population level, the lognormal model had the lowest AIC and BIC values.

plot_params <- function(prm_data, best_col){

  prm_data%>% 
  filter(., data == "POP") %>% 
  dplyr::select(., estimate, sd) -> pop_est

  title <- paste(prm_data$dist, prm_data$param)

  if(best_col == "BIC"){
    prm_data %>% 
    filter(data != "POP") %>% 
    ggplot(., aes(x = data, y = estimate)) +
    #facet_grid(dist~param, switch = "y", scales = "free") +
    # geom_point() +
    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
    labs(x = "", y = "", subtitle = title) +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, color = prm_data$best_bic)) -> plot
  }

  if(best_col == "AIC"){
    prm_data %>% 
    filter(data != "POP") %>% 
    ggplot(., aes(x = data, y = estimate)) +
    #facet_grid(dist~param, switch = "y", scales = "free") +
    # geom_point() +
    # geom_errorbar(aes(ymin = estimate - sd, ymax = estimate + sd))+
    geom_pointrange(aes(ymin = estimate - sd, ymax = estimate + sd)) +
    geom_hline(aes(yintercept = pop_est$estimate), color = "blue") +
    geom_hline(aes(yintercept = pop_est$estimate + pop_est$sd), color = "blue", linetype = "dashed") +
    geom_hline(aes(yintercept = pop_est$estimate - pop_est$sd), color = "blue", linetype = "dashed") +
    labs(x = "", y = "", subtitle = title) +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, color = prm_data$best_aic)) -> plot
  }
  return(plot)

}

```{r fig.height=10, fig.width=12}

nice_prms %>% 
  filter(., dist == "Exponential") %>% 
  plot_params(., best_col = "BIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p1

nice_prms %>% 
  filter(., dist == "Gamma" & param == "SHAPE") %>% 
  plot_params(., best_col = "BIC") +
  #theme(axis.text.x = element_blank()) +
  NULL -> p2

nice_prms %>% 
  filter(., dist == "Gamma" & param == "RATE") %>% 
  plot_params(., best_col = "BIC") +
  #theme(axis.text.x = element_blank()) +
  NULL -> p3

nice_prms %>% 
  filter(., dist == "Weibull" & param == "SHAPE") %>% 
  plot_params(., best_col = "BIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p4

nice_prms %>% 
  filter(., dist == "Weibull" & param == "SCALE") %>% 
  plot_params(., best_col = "BIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p5

nice_prms %>% 
  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
  plot_params(., best_col = "BIC") -> p6

nice_prms %>% 
  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
  plot_params(., best_col = "BIC") ->p7

plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> bic_grid

nice_prms %>% 
  filter(., dist == "Exponential") %>% 
  plot_params(., best_col = "AIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p1

nice_prms %>% 
  filter(., dist == "Gamma" & param == "SHAPE") %>% 
  plot_params(., best_col = "AIC") +
  #theme(axis.text.x = element_blank()) +
  NULL -> p2

nice_prms %>% 
  filter(., dist == "Gamma" & param == "RATE") %>% 
  plot_params(., best_col = "AIC") +
  #theme(axis.text.x = element_blank()) +
  NULL -> p3

nice_prms %>% 
  filter(., dist == "Weibull" & param == "SHAPE") %>% 
  plot_params(., best_col = "AIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p4

nice_prms %>% 
  filter(., dist == "Weibull" & param == "SCALE") %>% 
  plot_params(., best_col = "AIC") +
  #theme(axis.text.x = element_blank()) +
  NULL-> p5

nice_prms %>% 
  filter(., dist == "Lognormal" & param == "MEANLOG") %>% 
  plot_params(., best_col = "AIC") -> p6

nice_prms %>% 
  filter(., dist == "Lognormal" & param == "SDLOG") %>% 
  plot_params(., best_col = "AIC") ->p7

plot_grid(p1, NULL, p2, p3, p4, p5, p6, p7, ncol = 2, align = "v") -> aic_grid

plot_grid(bic_grid, aic_grid, ncol = 2)

#References

>>>>

@@

@@

# Example: Many-banded aracari movement

```{r setup, include=FALSE}
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, 
                      #eval=FALSE,
                      echo = FALSE)

@@

```{r}
aracari_df %>% 
  mutate(nu = dist/(dt/60)) %>% 
  dplyr::select(id, nu, rel.angle, dt) %>% 
  drop_na(nu) %>% 
  mutate(B_id = paste0("B", id))-> df

# Select individuals with at least 30 data points for velocity
df %>% 
  dplyr::select(id, nu) %>% 
  group_by(id) %>% 
  tally() %>% 
  filter(., n >= 30) %>% 
  dplyr::pull(id) -> nu_id

# Select individuals with 20 or 30? angles
df %>% 
  dplyr::select(id, rel.angle, dt) %>%
  mutate(dt = dt/60) %>% 
  drop_na(rel.angle) %>% 
  #filter(., dt == 15) %>% 
  group_by(id) %>% 
  tally() %>% 
  filter(., n >= 25) %>% 
  dplyr::pull(id) -> angle_id

@@

nu_df <- df %>% 
  dplyr::filter(nu != 0,
                id %in% nu_id) %>% 
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360))

dist.used <- c( "exp", "gamma", "weibull", "lnorm")
param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")
kpars <- c(1, 2, 2, 2, 2, 2, 2)

@@

\newpage
Figure 1. Probability densities of velocities for each individual bird (gray lines) compared to the complete pooling of data (light blue).

```{r}
nu_df %>%
  ggplot(., aes((x = nu))) +
  geom_line(aes(x = nu, group = id), stat = "density", alpha = 0.4) +
  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in meters/minute") +
  theme_classic()
```

Figure 2. Probability densities of turning angles in radians

```{r}
nu_df %>% 
  drop_na(rel.angle) %>% 
  ggplot(., aes(x = rel.angle)) +
  geom_line(aes(x =  rel.angle, group = id), stat = "density", alpha = 0.4) +
  geom_line(stat = "density", color = "#1191d1", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Turning angle in radians")
```

Figure 3. Comparison between histograms of turning angles in degrees for individuals versus complete pooling of data.

```{r}
p1_angles <- nu_df %>% 
  drop_na(d.angle) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  labs(title = "Complete pooling")

p2_angles <- nu_df %>% 
  drop_na(d.angle) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  facet_wrap(~B_id) +
  theme(axis.text = element_blank()) +
  labs(title = "No pooling")

plot_grid(p1_angles, p2_angles)

@@

@@

pop <- lapply(dist.used, function(x){fitdist(nu_df$nu, distr = x)})

@@

# Repeating the process for data at the individual level
inds <- unique(as.character(nu_df$B_id))

# Fitting the four distributions for each individual and saving the parameters in a dataframe
ind.models <- NULL
for(i in 1:length(inds)){
  fit.df <- nu_df %>% 
    dplyr::filter(., B_id == inds[i])

  fit <- lapply(dist.used, function(x){fitdist(fit.df$nu, distr = x)})

@@

Figure 4. QQplot fits of each distribution model to the velocity data

@@

qqpop %>% 
  mutate(individual = "Complete Pooling") %>% 
  ggplot(., aes(x = theoretical, y = empirical, color = fdist)) +
  facet_wrap(~individual) +
  #coord_equal() +
  geom_point(shape = 16, alpha = 0.8, size = 4) +
  geom_abline(intercept = 0, slope = 1) +
  labs(x = "Model Quantiles",
         y = "Empirical Quantiles") +
  #scale_color_viridis_d() +
  scale_color_brewer(palette = "Spectral", name = "Distribution") +
  theme(legend.position = c(0.8, 0.2)) +
  NULL -> a

@@

```
## Information criteria

@@

prms.df %>% 
  mutate(param = str_to_upper(param), 
         dist = str_replace(dist, "exp", "Exponential"),
         dist = str_replace(dist, "gamma", "Gamma"),
         dist = str_replace(dist, "weibull", "Weibull"),
         dist = str_replace(dist, "lnorm", "Lognormal"),
         data = str_replace(data, "pop", "POP")) %>% 
  mutate(BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
  mutate(best_bic = ifelse(deltaBIC == 0, "#ffaa00", "black"),
         best_aic = ifelse(deltaAIC == 0, "#fc0362", "black")) -> nice_prms

nice_prms %>% 
  filter(., str_detect(data, "B")) %>% 
  dplyr::select(dist, data, deltaAIC,
                #deltaAICc,
                deltaBIC) %>% 
  distinct() %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  filter(value == 0) %>%  
  pivot_wider(., names_from = ic, values_from = dist) %>% 
  mutate(agree = ifelse(deltaAIC == deltaBIC, paste(deltaBIC), paste(deltaBIC, "(BIC),", deltaAIC, "(AIC)"))) %>% 
  dplyr::select(., data, agree) %>% 
  rename(Individual = data,
            `Best model` = agree) -> best_model

# knitr::kable(best_model)
```

```{r fig.width=12, fig.height=4}
# To visualize the differences in the information criteria at the individual level

@@

@@

```{r}
# Table for BIC and AIC only

@@

gt_tbl %>% 
  tab_header(
    title = md("**Model comparisons across levels**")
  ) %>% 
  tab_stubhead(label = "Model") %>% 
  tab_row_group(
    group = "No Pooling",
    rows = 9
  ) %>% 
  tab_row_group(
    group = "Partial Pooling",
    rows = 1:4
  ) %>% 
  tab_row_group(
    group = "Complete Pooling", 
    rows = 5:8
  ) %>% 
  tab_spanner(
    label = md("**BIC**"),
    columns = vars(BIC, delta_BIC_within, delta_BIC_across)
  ) %>% 
  tab_spanner(
    label = md("**AIC**"),
    columns = vars(AIC, delta_AIC_within, delta_AIC_across)
  ) %>% 
  cols_label(
    delta_BIC_within = html("&Delta; BIC<sub>within</sub>"),
    delta_BIC_across = html("&Delta; BIC<sub>across</sub>"),
    delta_AIC_within = html("&Delta; AIC<sub>within</sub>"),
    delta_AIC_across = html("&Delta; AIC<sub>across</sub>")
  ) -> gt_table_bic

@@

# References
